Tor's Usability for Censorship Circumvention

### 2015-04-16 PETS2015-paper/paper.tex
I guess some people don't like contractions.
Period after "etc".

We ran a small pilot study of five journalists which involved a cognitive walk through in which 
participants explained the motivation for their actions and any confusion that they had during the process. 
We did this to find new stopping points, and sources of confusion. 
But in the process, we were also able to observe how users would download Tor, 
if they could understand the address bar/menu, how well they were able to complete basic tasks
(searching, setting new circuits, etc), and generally if they had any usability complaints about the browser.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Targeting specific pluggable transports.}
Some pluggable transports work in censorship environments
where others don't.
Also, some of them require additional information
(like bridge addresses) before they can work.
Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports?

>>>>

We ran a small pilot study of five journalists which involved a cognitive walk through in which 
participants explained the motivation for their actions and any confusion that they had during the process. 
We did this to find new stopping points, and sources of confusion. 
But in the process, we were also able to observe how users would download Tor, 
if they could understand the address bar/menu, how well they were able to complete basic tasks
(searching, setting new circuits, etc.), and generally if they had any usability complaints about the browser.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Targeting specific pluggable transports.}
Some pluggable transports work in censorship environments
where others do not.
Also, some of them require additional information
(like bridge addresses) before they can work.
Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports?
